---
title: "ultra"
author: "Joe Butler"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    fig_width: 8
    fig_height: 5
vignette: >
  %\VignetteIndexEntry{ultra}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---
  
<style type="text/css">
.main-container {
  max-width: 768px;
  margin-left: auto;
  margin-right: auto;
}
</style>  

# Getting Started

This section helps you get started with the ultra package.

```{r,include=FALSE}
knitr::opts_chunk$set(dev = "svg", fig.ext = "svg")
```

## Example Code
```{r plot, fig.height=6, echo=TRUE}
library(ultra)
load("J:/My Drive/BSI_FINAL/ULTRA/git2/ultra/R/results.Rdata")
ULTRAplot(results)
```


## Citing ultra
This package was developed through research performed in the <a href="https://www.amc.nl/web/research-75/departments/center-for-experimental-and-molecular-medicine-cemm.htm" target="_blank" rel="noopener noreferrer">Center for Experimental and Molecular Medicine</a> at the Amsterdam University Medical Center.

If you use this package please cite using:

```{r,include=T}
 citation("ultra")
```

Thank you to the following collaborators, without whose support this work would not have been possible:<br>
<a href="https://immunexpress.com/" target="_blank" rel="noopener noreferrer">Immunexpress</a><br>
<a href="https://www.arcsepsis.com/" target="_blank" rel="noopener noreferrer">The African Research Collaboration on Sepsis</a>

